---
title: "Analysis"
author: "Vasco"
output: 
  html_document:
    code_folding: hide
---

```{r, echo = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


```{r}
library(targets)
library(ordinal)
library(rempsyc)
library(flextable)
library(gtsummary)
```

I used NCHAT data to investigate differences in financial abuse between gender. Using only primary participants, I looked at item Q129D, which asked how often the person's partner "Kept [them] from having access to a job, money, or financial resources."

The following table breaks down responses given by cis men and women, as the data for transgender people did not indicate a gender ("transgender", the only option to analyse, is not a gender). 

```{r}
tar_load(table)

table
```

We can see that the overwhelming majority of participants of both genders indicate never being subject to financial abuse. The following plot make this stark similarity more obvious:

```{r}
tar_load(plot)

plot
```

To formally analyze differences, I also ran an ordinal model predicting responses, whose coefficients are summarized next:

```{r}
tar_load(summary)

summary
```

We find no statistical evidence for a difference between men and women (OR = 0.83, 95% CI [0.59, 1.16], p = .3).

Below, the default model summary provided by R.

```{r}
tar_load(model)

summary(model)
```

